GVN-Hoist: Hoisting Computations from Branches

### 2016-08-19 hoist.tex
static metrics

\section{Experimental Evaluation}
\label{sec:experimental-results}
We ran llvm-testsuite (trunk:d87471f8) with the patch (trunk:86940146 and the
results are listed in Table-\ref{tab:results}. The table lists the number of
scalars, loads, stores and calls hoisted as well as removed. For each category,
the number of instructions removed is greater or equal to the number of
instructions hoisted because each hoisting is performed only when at least one
identical computation is found.

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|c|}
      \hline
      Metric               & Number\\\hline
      Scalars hoisted      & 6791  \\\hline
      Scalars removed      & 9696  \\\hline
      Loads hoisted        & 14802 \\\hline
      Loads removed        & 20719 \\\hline
      Stores hoisted       & 15    \\\hline
      Stores removed       & 15    \\\hline
      Calls hoisted        & 8     \\\hline
      Calls removed        & 8     \\\hline
      Total Instructions hoisted & 21616 \\\hline
      Total Instructions removed & 30438 \\\hline
\end{tabular}
  \end{center}
  \caption{Code hoisting metrics on llvm-testsuite}
  \label{tab:results}
\end{table}

>>>>

\section{Experimental Evaluation}
\label{sec:experimental-results}
We ran llvm-testsuite (trunk:d87471f8) with the patch (trunk:86940146 and the
results are listed in Table-\ref{tab:hoist-results}. The table lists the number
of scalars, loads, stores and calls hoisted as well as removed. For each
category, the number of instructions removed is greater or equal to the number
of instructions hoisted because each hoisting is performed only when at least
one identical computation is found.

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|c|}
      \hline
      Metric               & Number\\\hline
      Scalars hoisted      & 6791  \\\hline
      Scalars removed      & 9696  \\\hline
      Loads hoisted        & 14802 \\\hline
      Loads removed        & 20719 \\\hline
      Stores hoisted       & 15    \\\hline
      Stores removed       & 15    \\\hline
      Calls hoisted        & 8     \\\hline
      Calls removed        & 8     \\\hline
      Total Instructions hoisted & 21616 \\\hline
      Total Instructions removed & 30438 \\\hline
\end{tabular}
  \end{center}
  \caption{Code hoisting metrics on llvm-testsuite}
  \label{tab:hoist-results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|c|c|}
      \hline
      Metric               & Before & After              \\\hline
      Call sites deleted, not inlined             & 1988    & 1988   \\\hline
      Functions deleted (all callers found)       & 38250   & 38255  \\\hline
      Functions inlined                           & 154986  & 154985 \\\hline
      Allocas merged together                     & 212     & 212    \\\hline
      Caller-callers analyzed                     & 193042  & 193092 \\\hline
      Call sites analyzed                         & 414336  & 414381 \\\hline
      Rematerialized defs for spilling            & 18321   & 18326  \\\hline
      Rematerialized defs for splitting           & 5719    & 5842   \\\hline
      Spill slots allocated                       & 42912   & 42970  \\\hline
      Spilled live ranges                         & 61330   & 61362  \\\hline
      Spills inserted                             & 50724   & 50784  \\\hline
\end{tabular}
  \end{center}
  \caption{Static metrics before and after code-hoisting on llvm-testsuite}
  \label{tab:static-results}
\end{table}

Other static metrics are listed in Table-\ref{tab:static-results}. Here we can
see that except for rematerializing defs for splitting, which has an overhead of ~2\%, all
other parameters have less than 1\% overhead. This is to explain why the performance does not
go down with our implementation (and cost-model) of code hoisting pass.
